---
title: "Manual Filter"
output: html_document
---

#Collecting all the Data

Effectively running JSONParseR.R

```{r, include=FALSE}
library(dplyr)
library(tidyr)
library(mosaic)
library(tidyjson)
library(readr)
library(lubridate)
```

```{r, include=FALSE}
text <- read_file("Data/data1.txt")
list <- unlist(strsplit(text, "\n"))   #One auction per row
small <- sample(list, size=10000, replace=FALSE)
```

```{r, include=FALSE}
event <- small %>% as.tbl_json %>%
  enter_object("em") %>%
  spread_values(timestamp = jnumber("t"),
                country = jstring("cc"),
                region = jstring("rg"))
event <- event %>%
  mutate(timestamp = round(timestamp, 10)/1000) %>%
  mutate(timestamp = as.POSIXct(timestamp, origin = "1970-01-01",tz = "GMT")) %>%
  mutate(dayofweek = wday(timestamp)) %>%
  mutate(hour = hour(timestamp)) %>%
  mutate(month = month(timestamp)) %>%
  select(-timestamp)

auction <- small %>% as.tbl_json %>%
  enter_object("auction") %>%
  spread_values(margin = jnumber("margin"),
                tmax = jnumber("tmax")) %>%
  enter_object("user") %>%
  spread_values(bluekai = jstring("bkc"))
auction <- auction %>%
  mutate(bluekai = !is.na(bluekai))

site <- small %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("site") %>%
  spread_values(sitetype = jstring("typeid"),
                sitecat = jstring("cat")) %>%
  enter_object("publisher") %>%
  spread_values(pubID = jstring("id"))

bidreq <- small %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bidrequests") %>%
  gather_array() %>%
  spread_values(reqID1 = jstring("id"),
                vertical = jstring("verticalid"),
                dsp = jstring("bidderid")) %>%   #Don't use if we're making 35 algorithms
  enter_object("impressions") %>%
  gather_array() %>%
  spread_values(bidfloor = jnumber("bidfloor"),
                adformat = jstring("format"),
                adproduct = jstring("product")) %>%
  enter_object("banner") %>%
  spread_values(width = jnumber("w"),
                height = jnumber("h"))
bidreq <- bidreq %>%
  filter(dsp != "35" & dsp != "37") %>% 
  filter(adformat != "1" &
           adformat != "2" &
           adformat != "3" &
           adformat != "4" &
           adformat != "6" &
           adformat != "7" &
           adformat != "20" &
           adformat != "21" &
           adformat != "22" & 
           adformat != "25" & 
           adformat != "26")

bid <- small %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bids") %>%
  gather_array %>%
  spread_values(reqID2 = jstring("requestid"),
                winner = jstring("winner"))
```

```{r, include=FALSE}
full <- bidreq %>%
  left_join(auction, by="document.id") %>%
  left_join(event, by="document.id") %>%
  left_join(site, by="document.id") %>%
  left_join(bid, by="document.id")
full <- as.data.frame(full)
full <- full %>%
  mutate(responded = reqID1==reqID2) %>%
  mutate(realwinner = responded & winner == "TRUE") %>%
  select(-winner)
full[["realwinner"]][is.na(full[["realwinner"]])] <- 0
full[["responded"]][is.na(full[["responded"]])] <- 0
full <- full %>%
  select(-reqID1) %>%
  select(-reqID2)
full <- full %>%
  mutate(responded = responded == 1) %>%
  mutate(realwinner = realwinner == 1)
```

#Filtering

Here we construct filters based solely on interesting variables found in the data. The baseline proportions of impression success for the data are:

```{r}
round(tally(full$realwinner, format="proportion"),3)
```

##Filter 1

Now we apply a filter:
- Randomly filter 20% from 10-4
- Cut out DSPs 19, 10, 28, 25, 34, 36

```{r}
clean <- full %>%
  filter(dsp != "19" &
           dsp != "10" &
           dsp != "28" &
           dsp != "25" &
           dsp != "34" &
           dsp != "36")
clean1 <- clean %>%
  filter(hour >= 10 &
           hour <= 16) %>%
  sample_frac(0.8, replace=FALSE)
clean2 <- clean %>%
  filter(hour <10 |
           hour > 16)
clean <- bind_rows(clean1, clean2)
```

```{r}
round(tally(clean$realwinner, format="proportion"),3)
```

Now we construct a confusion matrix

```{r}
confmat <- matrix(c(0,0,0,0), nrow=2, ncol=2)
confmat[1,1] <- sum(!full$realwinner) - sum(!clean$realwinner)
confmat[1,2] <- sum(full$realwinner) - sum(clean$realwinner)
confmat[2,1] <- sum(!clean$realwinner)
confmat[2,2] <- sum(clean$realwinner)
confmat
```

```{r}
#|TN|FN|
#|--|--|
#|FP|TP|
```

```{r}
recall <- confmat[2,2]/(confmat[2,2]+confmat[1,2]); recall
filtered <- sum(confmat[1,])/sum(confmat); filtered
```

##Filter 2

What happens if we don't randomly filter during peak hours?
We apply a filter:
- Cut out DSPs 19, 10, 28, 25, 34, 36

```{r}
clean <- full %>%
  filter(dsp != "19" &
           dsp != "10" &   # Without this it's 20% filtering, 100% recall
           dsp != "28" &
           dsp != "25" &
           dsp != "34" &
           dsp != "36")
round(tally(clean$realwinner, format="proportion"),3)
```

Now we construct another confusion matrix

```{r}
confmat <- matrix(c(0,0,0,0), nrow=2, ncol=2)
confmat[1,1] <- sum(!full$realwinner) - sum(!clean$realwinner)
confmat[1,2] <- sum(full$realwinner) - sum(clean$realwinner)
confmat[2,1] <- sum(!clean$realwinner)
confmat[2,2] <- sum(clean$realwinner)
confmat
```

```{r}
#|TN|FN|
#|--|--|
#|FP|TP|
```

```{r}
recall <- confmat[2,2]/(confmat[2,2]+confmat[1,2]); recall
filtered <- sum(confmat[1,])/sum(confmat); filtered
```

##Filter 3

What happens if we only keep 6 DSPs?
We apply a filter:
- Keep only DSPs 1, 2, 5, 14, 27, 29

```{r}
cleaner <- full %>%
  filter(dsp == "1" |
           dsp == "4" |
           dsp == "5" |
           dsp == "14" |
           dsp == "27" |
           dsp == "29")
round(tally(cleaner$realwinner, format="proportion"),3)
```

```{r}
confmat <- matrix(c(0,0,0,0), nrow=2, ncol=2)
confmat[1,1] <- sum(!full$realwinner) - sum(!cleaner$realwinner)
confmat[1,2] <- sum(full$realwinner) - sum(cleaner$realwinner)
confmat[2,1] <- sum(!cleaner$realwinner)
confmat[2,2] <- sum(cleaner$realwinner)
confmat
```

```{r}
#|TN|FN|
#|--|--|
#|FP|TP|
```

```{r}
recall <- confmat[2,2]/(confmat[2,2]+confmat[1,2]); recall
filtered <- sum(confmat[1,])/sum(confmat); filtered
```

