---
title: "Finding differences between May and June"
output: html_document
---

```{r}
text <- read_file("Data/data0.txt")
maylist <- unlist(strsplit(text, "\n"))   #One auction per row
may <- sample(maylist, size=10000, replace=FALSE)

text <- read_file("Data/newdata0.txt")
junelist <- unlist(strsplit(text, "\n"))   #One auction per row
june <- sample(junelist, size=10000, replace=FALSE)
```



```{r}
mayevent <- may %>% as.tbl_json %>%
  enter_object("em") %>%
  spread_values(timestamp = jnumber("t"),
                country = jstring("cc"),
                region = jstring("rg"))
mayevent <- mayevent %>%
  mutate(timestamp = round(timestamp, 10)/1000) %>%   # Cut off milliseconds
  mutate(timestamp = as.POSIXct(timestamp, origin = "1970-01-01",tz = "GMT")) %>%
  mutate(dayofweek = wday(timestamp)) %>%
  mutate(hour = hour(timestamp)) %>%
  mutate(month = month(timestamp)) %>%
  select(-timestamp)

mayauction <- may %>% as.tbl_json %>%
  enter_object("auction") %>%
  spread_values(margin = jnumber("margin"),
                tmax = jnumber("tmax")) %>%
  enter_object("user") %>%
  spread_values(bluekai = jstring("bkc"))
mayauction <- mayauction %>%
  mutate(bluekai = !is.na(bluekai))

maysite <- may %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("site") %>%
  spread_values(sitetype = jstring("typeid"),
                sitecat = jstring("cat")) %>%
  enter_object("publisher") %>%
  spread_values(pubID = jstring("id"))


maybidreq <- may %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bidrequests") %>%
  gather_array() %>%
  spread_values(reqID = jstring("id"),
                vertical = jstring("verticalid"),
                dsp = jstring("bidderid")) %>%
  enter_object("impressions") %>%
  gather_array() %>%
  spread_values(bidfloor = jnumber("bidfloor"),
                adformat = jstring("format"),
                adproduct = jstring("product"))   # array.index is impID
                                                  # ignore bid requests w/o impressions
maybanner <- may %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bidrequests") %>%
  gather_array() %>%
  spread_values(reqID = jstring("id")) %>%
  enter_object("impressions") %>%
  gather_array() %>%
  enter_object("banner") %>%
  spread_values(width = jnumber("w"),
                height = jnumber("h"))   # array.index is impID

maybid <- may %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bids") %>%
  gather_array %>%
  spread_values(reqID = jstring("requestid"),
                array.index = jstring("impid"),
                winner = jstring("winner"))
maybid <- maybid %>%
  mutate(winner = !is.na(winner))   #response is win

maybanner <- maybanner %>%
  select(-document.id)
maybid <- maybid %>%
  select(-document.id)

foo <- maybidreq %>%
  left_join(maybanner, by=c("reqID", "array.index")) %>%
  left_join(maybid, by=c("reqID", "array.index"))

mayfull <- foo %>%
  left_join(mayevent, by="document.id") %>%
  left_join(mayauction, by="document.id") %>%
  left_join(maysite, by="document.id") %>%
  rename(Auction=document.id, BidReq=array.index)
mayfull <- mayfull %>%
  select(-reqID)
mayfull <- mayfull[c("Auction","country","region","dayofweek","hour","month",
                         "margin","tmax","bluekai","sitetype","sitecat","pubID",
                         "BidReq","dsp","vertical",
                         "bidfloor","adformat","adproduct","width","height","winner")]

mayfull <- mayfull %>%
  filter(dsp != "35" & dsp != "37") %>%   # Filter out DSPs we should ignore
  filter(adformat != "1" &   # Filter out Ad Formats we should ignore
           adformat != "2" &
           adformat != "3" &
           adformat != "4" &
           adformat != "6" &
           adformat != "7" &
           adformat != "20" &
           adformat != "21" &
           adformat != "22" & 
           adformat != "25" & 
           adformat != "26")
```


```{r}
juneevent <- june %>% as.tbl_json %>%
  enter_object("em") %>%
  spread_values(timestamp = jnumber("t"),
                country = jstring("cc"),
                region = jstring("rg"))
juneevent <- juneevent %>%
  mutate(timestamp = round(timestamp, 10)/1000) %>%   # Cut off milliseconds
  mutate(timestamp = as.POSIXct(timestamp, origin = "1970-01-01",tz = "GMT")) %>%
  mutate(dayofweek = wday(timestamp)) %>%
  mutate(hour = hour(timestamp)) %>%
  mutate(month = month(timestamp)) %>%
  select(-timestamp)

juneauction <- june %>% as.tbl_json %>%
  enter_object("auction") %>%
  spread_values(margin = jnumber("margin"),
                tmax = jnumber("tmax")) %>%
  enter_object("user") %>%
  spread_values(bluekai = jstring("bkc"))
juneauction <- juneauction %>%
  mutate(bluekai = !is.na(bluekai))

junesite <- june %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("site") %>%
  spread_values(sitetype = jstring("typeid"),
                sitecat = jstring("cat")) %>%
  enter_object("publisher") %>%
  spread_values(pubID = jstring("id"))


junebidreq <- june %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bidrequests") %>%
  gather_array() %>%
  spread_values(reqID = jstring("id"),
                vertical = jstring("verticalid"),
                dsp = jstring("bidderid")) %>%
  enter_object("impressions") %>%
  gather_array() %>%
  spread_values(bidfloor = jnumber("bidfloor"),
                adformat = jstring("format"),
                adproduct = jstring("product"))   # array.index is impID
                                                  # ignore bid requests w/o impressions
junebanner <- june %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bidrequests") %>%
  gather_array() %>%
  spread_values(reqID = jstring("id")) %>%
  enter_object("impressions") %>%
  gather_array() %>%
  enter_object("banner") %>%
  spread_values(width = jnumber("w"),
                height = jnumber("h"))   # array.index is impID

junebid <- june %>% as.tbl_json %>%
  enter_object("auction") %>%
  enter_object("bids") %>%
  gather_array %>%
  spread_values(reqID = jstring("requestid"),
                array.index = jstring("impid"),
                winner = jstring("winner"))
junebid <- junebid %>%
  mutate(winner = !is.na(winner))   #response is win

junebanner <- junebanner %>%
  select(-document.id)
junebid <- junebid %>%
  select(-document.id)

foo <- junebidreq %>%
  left_join(junebanner, by=c("reqID", "array.index")) %>%
  left_join(junebid, by=c("reqID", "array.index"))

junefull <- foo %>%
  left_join(juneevent, by="document.id") %>%
  left_join(juneauction, by="document.id") %>%
  left_join(junesite, by="document.id") %>%
  rename(Auction=document.id, BidReq=array.index)
junefull <- junefull %>%
  select(-reqID)
junefull <- junefull[c("Auction","country","region","dayofweek","hour","month",
                         "margin","tmax","bluekai","sitetype","sitecat","pubID",
                         "BidReq","dsp","vertical",
                         "bidfloor","adformat","adproduct","width","height","winner")]

junefull <- junefull %>%
  filter(dsp != "35" & dsp != "37") %>%   # Filter out DSPs we should ignore
  filter(adformat != "1" &   # Filter out Ad Formats we should ignore
           adformat != "2" &
           adformat != "3" &
           adformat != "4" &
           adformat != "6" &
           adformat != "7" &
           adformat != "20" &
           adformat != "21" &
           adformat != "22" & 
           adformat != "25" & 
           adformat != "26")
```

# Examining winrates

Overall, our conclusion is that June winrates are much higher than May winrates.

```{r}
dim(mayfull)[1]
dim(junefull)[1]
```
There are significantly more impressions per auction in May than there are in June

```{r}
tally(mayfull$winner, format="proportion")
tally(junefull$winner, format="proportion")
```
It definitely seems like June impressions are more likely to win

```{r}
foo <- mayfull %>%
  group_by(Auction) %>%
  summarize(winner=sum(winner, na.rm=TRUE))
tally(foo$winner)

bar <- junefull %>%
  group_by(Auction) %>%
  summarize(winner=sum(winner, na.rm=TRUE))
tally(bar$winner)
```
June auctions are more likely to win too. With fewer impressions per auction, this is surprising.

# Examining distributions

```{r}
# Plot impression success rate by DSP
foo <- mayfull %>%
  select(dsp, winner) %>%
  group_by(dsp) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(foo, aes(x=reorder(dsp, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))

# Plot impression success rate by DSP
bar <- junefull %>%
  select(dsp, winner) %>%
  group_by(dsp) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(bar, aes(x=reorder(dsp, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
```

```{r}
# Plot impression success rate by DSP
foo <- mayfull %>%
  select(dsp, winner) %>%
  group_by(dsp) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(foo, aes(x=reorder(dsp, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))

# Plot impression success rate by DSP
bar <- junefull %>%
  select(dsp, winner) %>%
  group_by(dsp) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(bar, aes(x=reorder(dsp, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
```

```{r}
foo <- mayfull %>%
  select(hour, winner) %>%
  group_by(hour) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3))
ggplot(foo, aes(x=hour, y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1)
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
  
tally(mayfull$hour)

bar <- junefull %>%
  select(hour, winner) %>%
  group_by(hour) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3))
ggplot(bar, aes(x=hour, y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) + 
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
  
  scale_fill_gradient2(mid="#818285", high="#F2B518")
```

```{r}
foo <- mayfull %>%
  select(country, winner) %>%
  group_by(country) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3))
foo <- foo %>%
  filter(num > 100)
ggplot(foo, aes(x=country, y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1)
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
  
tally(mayfull$hour)

bar <- junefull %>%
  select(country, winner) %>%
  group_by(country) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3))
bar <- bar %>%
  filter(num > 100)
ggplot(bar, aes(x=country, y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) + 
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
```

```{r}
foo <- mayfull %>%
  filter(tmax < 200)
ggplot(mayfull, aes(tmax)) +
  geom_histogram()
ggplot(foo, aes(tmax)) +
  geom_histogram(bins=10)

bar <- junefull %>%
  filter(tmax < 200)
ggplot(junefull, aes(tmax)) +
  geom_histogram()
ggplot(bar, aes(tmax)) +
  geom_histogram(bins=10)
```
```{r}
ggplot(mayfull, aes(margin)) +
  geom_histogram()
ggplot(junefull, aes(margin)) +
  geom_histogram()
```

```{r}
foo <- mayfull %>%
  select(adformat, winner) %>%
  group_by(adformat) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(foo, aes(x=reorder(adformat, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))

bar <- junefull %>%
  select(adformat, winner) %>%
  group_by(adformat) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(bar, aes(x=reorder(adformat, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
```

```{r}
foo <- mayfull %>%
  select(sitetype, winner) %>%
  group_by(sitetype) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(foo, aes(x=reorder(sitetype, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))

bar <- junefull %>%
  select(sitetype, winner) %>%
  group_by(sitetype) %>%
  summarize(num=n(), prop = round(sum(winner, na.rm=TRUE)/n(),3)) %>%
  arrange(prop)
ggplot(bar, aes(x=reorder(sitetype, prop), y=num, fill = prop, label=prop)) +
  geom_bar(stat="identity") +
  geom_text(vjust = -1) +
  scale_y_sqrt() +
  ggtitle("Success of Impressions by DSP") +
  xlab("DSP") +
  ylab("Sqrt Number of Impressions") +
  guides(fill=guide_legend(title="Proportion of \nSuccessful Impressions", reverse=TRUE))
```

```{r}

```


